Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-10-15 doc/JFLA2022/paper.tex
final pass over section 3.4 text

>>>>

Before the Ackermann sublibrary was moved from the Goedel package repository to the \Hydras repository, the Goedel package had around 7,000 specification LOC and 38,000 proof LOC. Figure~\ref{fig:genealogy} and Table~\ref{tbl:loc} thus reveal that the seemingly large Coq formalization of G\"{o}del's incompleteness theorem can be considered as a modestly-sized proof on top of general libraries for, on the one hand, first-order logic, primitive recursive functions, and Peano arithmetic (Ackermann), and on the other hand, prime numbers and their properties (Pocklington).
